formula1

### 2020-08-10 inst/formula1.Rmd
typo
bugfix

Formula 1 racing is an important and prestigious motor sport.  Here I
analyse a series of racing results using the `hyper` package which
implements the Plackett-Luce likelihood function.

@@

```{r,fouryearsdata, cache=TRUE}
F1_2014 <- "formula1_2014.txt" %>% read.table(header=TRUE) %>% ordertable2supp
F1_2015 <- "formula1_2015.txt" %>% read.table(header=TRUE) %>% ordertable2supp
F1_2016 <- "formula1_2016.txt" %>% read.table(header=TRUE) %>% ordertable2supp
F1_2017 <- "formula1_2017.txt" %>% read.table(header=TRUE) %>% ordertable2supp
a <- list(F1_2014, F1_2015, F1_2016, F1_2017)
alldrivers <- all_pnames(a)

>>>>

Formula 1 racing is an important and prestigious motor sport.  Here I
analyse a series of racing results using the `hyper2` package which
implements the Plackett-Luce likelihood function.

@@

```{r,fouryearsdata, cache=TRUE}

jj <- read.table("formula1_2014.txt",header=TRUE)
F1_2014 <- ordertable2supp(jj[,seq_len(ncol(jj)-1)], incomplete = TRUE)

jj <- read.table("formula1_2015.txt",header=TRUE)
F1_2015 <- ordertable2supp(jj[,seq_len(ncol(jj)-1)], incomplete = TRUE)

jj <- read.table("formula1_2016.txt",header=TRUE)
F1_2016 <- ordertable2supp(jj[,seq_len(ncol(jj)-1)], incomplete = TRUE)

jj <- read.table("formula1_2017.txt",header=TRUE)
F1_2017 <- ordertable2supp(jj[,seq_len(ncol(jj)-1)], incomplete = TRUE)

a <- list(F1_2014, F1_2015, F1_2016, F1_2017)
alldrivers <- all_pnames(a)
